\vspace{-2.5em} Excitation and Detection Efficiency of Ensembles of Molecules Under Polarized Illumination \vspace{-1em}

### 2017-09-20 notes/2017-09-19-ensemble-efficiencies/report/report.tex
Clarified that notes only consider polarized illumination.

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Excitation and Detection Efficiency of Ensembles of
  Molecules Under Polarized Illumination \vspace{-1em}} \author{Talon
  Chandler}% and Patrick La Rivi\`ere}
\date{\vspace{-1em}\today\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes I will calculate the excitation and detection efficiencies of
ensembles of molecules as a function of polarizer orientation and microscope
geometry. This work extends the results in the 2017-06-14 notes from single
molecules to ensembles of molecules.

@@

Similarly, the detection efficiency of an ensemble is
\begin{align}
  \eta_{\text{det}} = \int_{\mathbb{S}^2}d\mh{r} f(\mh{r}) \eta_{\text{det}}^{\text{single}} \label{eq:ensemble_det}%
\end{align} 
which is only true if the fluorophores emit light independently. I haven't given
the full expression for $\eta_{\text{det}}^{\text{single}}$ here---see the paper
or equation 2 with $D = 1$.

@@

\fig{../figures/single-frame.pdf}{1.0}{Representative examples of ensemble
  intensity measurements. Black dots indicate where the Cartesian unit vectors
  intersect the unit sphere. \newline \newline \textbf{Columns left to right:}
  1) fluorophore distributions with $\bs{\hat{\mu}} = \mb{\hat{z}}$ and varying
  $\kappa$; 2) microscope geometry schematics---all cases use two 0.8 NA
  objectives in a diSPIM geometry 3) the absorption efficiency as a function of
  $\bs{\hat{\mu}}$, see equation \ref{eq:ensemble}; 3) the detection efficiency
  as a function of $\bs{\hat{\mu}}$, see equation \ref{eq:ensemble_det}; (4) the
  total efficiency, the product of the absorption and detection
  efficiencies. \textbf{Note:} The last three columns do not use the same
  scale.}{single-frame}

>>>>

%%%%%%%%%%%%
% Document %
%%%%%%%%%%%%
\begin{document}
\title{\vspace{-2.5em} Excitation and Detection Efficiency of Ensembles of
  Molecules Under Polarized Illumination \vspace{-1em}} \author{Talon
  Chandler}% and Patrick La Rivi\`ere}
\date{\vspace{-1em}September 19, 2017\\ (Last Updated: \today)\vspace{-1em}}
\maketitle
\section{Introduction}
In these notes I will calculate the excitation and detection efficiencies of
ensembles of molecules as a function of polarizer orientation and microscope
geometry. This work extends the results in the 2017-06-14 notes from single
molecules to ensembles of molecules.

@@

Similarly, the detection efficiency of an ensemble is
\begin{align}
  \eta_{\text{det}} = \int_{\mathbb{S}^2}d\mh{r} f(\mh{r}) \eta_{\text{det}}^{\text{single}} \label{eq:ensemble_det}%
\end{align} 
which is only true if the fluorophores emit light independently. If the detector
uses a polarizer then $\eta_{\text{det}}^{\text{single}}$ is given by equation 2 with $D = 1$ (see Fourkas \cite{fourkas2001}). If the detector does not use a polarizer then
\begin{align}
  \eta_{\text{det}}^{\text{single}} = 2(A + B\sin^2\Theta).
\end{align}

@@

\fig{../figures/single-frame.pdf}{1.0}{Representative examples of ensemble
  intensity measurements. Black dots indicate where the Cartesian unit vectors
  intersect the unit sphere. \newline \newline \textbf{Columns left to right:}
  1) fluorophore distributions with $\bs{\hat{\mu}} = \mb{\hat{z}}$ and varying
  $\kappa$; 2) microscope geometry schematics---all cases use two 0.8 NA
  objectives in a diSPIM geometry with polarized illumination and unpolarized
  detection 3) the absorption efficiency as a function of $\bs{\hat{\mu}}$, see
  equation \ref{eq:ensemble}; 3) the detection efficiency as a function of
  $\bs{\hat{\mu}}$, see equation \ref{eq:ensemble_det}; (4) the total
  efficiency, the product of the absorption and detection
  efficiencies. \textbf{Note:} The last three columns do not use the same
  scale.}{single-frame}
